Total Platform Cyber Protection

### 2016-08-21 paper.tex
added till os, fixed biblio till os

>>>>

\section{Operating Systems}

The Operating System layer is responsible for ensuring that multiple
applications are able to concurrently run, without interfering with
each other. In addition, the Operating System layer is also
responsible for providing a unified abstraction of the underlying
hardware layer for the application layer. Therefore, in terms of
security, the Operating System layer has more privileges than the
application layer, as the Operating System controls the execution and
scheduling of processes, the access control policies that allow one
application to hide information/data from the other processes.

The main threat to the Operating System layer is an attacker
compromising the security of the Operating System. There are two main
avenues to how this compromise can occur: (1) an attacker exploits a
vulnerability in the Operating System from the Application layer or
(2) an attacker compromises a lower layer (for instance, modifying the
Operating System code directly to the hardware's Hard Drive).

Vulnerabilities in the Operating System allow an attacker to have
complete control over the other application running in the operating
system. In addition, the attacker can use their vantage point at the
operating system to attempt to escalate their attack to the hypervisor
or lower layers, such as the firmware. Vulnerabilities in the
Operating System result from programming errors that allow an attacker
to gain control of the Operating System code or data. These
vulnerabilities are traditional memory corruption vulnerabilities or
even logic flaws.

A main concern in Operating System security is the presence of
rootkits, which are malicious modifications to the Operating System
which an attacker uses to achieve persistence on the system. In
addition, attackers use rootkits to hide from other applications on
the system. For instance, the rootkit will modify the operating system
code such that the attacker's processes and files are hidden from the
administrator or defensive software installed on the Operating System,
such as an anti-virus solution.

Direct access to the hardware can allow an attacker to compromise the
Operating System. It is in this way that an attacker can propagate
their compromise from the lower layers of the computing platform to
the upper layers. The attacker has similar capabilities as when
exploiting a vulnerability in the Operating system.

Research into Operating System security has a long and rich history,
which has looked at design flaws in Operating
Systems~\cite{attanasio1973}. Further research looked at reducing the
permissions of the \emph{root} users, essentially compartmentalizing
the privilege of the Operating System~\cite{kamp2000,kurmus2014a}.

Rootkits attempt to persist the attacker's compromise of the operating
system and allow them to hide their malicious behavior from other
applications on the system. Therefore, rootkit detection is an
important research topic in Operating System
security~\cite{petroni2004,wang2005,petroni2007,payne2008,sharif2009,yin2010,bianchi2012}.
Another approach is to prevent
the rootkit from altering the Operating System
kernel~\cite{riley2008,wang2009,grace2010,gadaleta2011}.

Vulnerability analysis techniques have been used to discover
vulnerabilities in the Operating System kernel before a hacker is able
to use and exploit those vulnerabilities. Static analysis techniques
have been used~\cite{chou2001,chen2011}.

Other vulnerability defenses include defenses for specific
vulnerability classes, such as buffer overflows~\cite{dalton2008}.
Randomization techniques attempt to alter the environment of the
operating system in such a way that the system continues to function
but the attacker's exploit fails~\cite{lin2009,giuffrida2012}.
Control-flow integrity techniques have been applied to Operating
System code as well~\cite{li2011a}.

Other research into Operating System security has looked at how to
protect applications from a malicious or compromised Operating
System~\cite{ta-min2006,onarlioglu2013,li2014}.

% either driver code execute or change `and' to `is'
As driver code executes in kernel space, and is a frequent source of
vulnerabilities~\cite{kadav2012}, researchers have looked into how to
make drivers more robust~\cite{ganapathy2008,hruby2012} or isolated
from the rest of the kernel~\cite{boyd-wickizer2010}.

Attack papers show that it is possible to compromise the kernel
without injecting any additional code, using Return Oriented
Programming techniques~\cite{hund2009}.

A completely different approach is to formally prove the correctness
of the Operating System kernel~\cite{klein2009}.

Updating Operating Systems with security updates is frequently
difficult, as the Operating System must be restarted. However,
researchers have explored how to apply an update to the Operating
System without rebooting the system~\cite{arnold2009}.

Some work has been done on removing the operating system
entirely~\cite{madhavapeddy2010} or trimming/tailoring parts of the
Operating System~\cite{kurmus2011,madhavapeddy2013,howell2013,kurmus2013,kurmus2014}.
This has the security benefit of reducing
the attack surface of the Operating System.

We believe that, while significant research has been done on the
Operating System layer, there still remains work to be done in this
area. In particular, as the Operating System is frequently in contact
with malicious applications, it must be hardened from attack.

Therefore, we believe that further research into the line of trimming
or tailoring the operating system is important, such that the attack
surface is significantly reduced.

We also believe that non-control data-flow attacks will be the new
wave of attacks against Operating Systems. Therefore, we need new
analysis techniques, both static and dynamic, to discover these
vulnerabilities that do not require altering the control flow of the
Operating System.

A critical component of the Operating System is to handle the
execution of concurrent applications. Therefore, attacks that take
advantage of the concurrency in the Operating System are unexplored.
Research must be done to create new models for these attacks.
